---
title: "Abacavirinol"
author: "Gloria Hernandez"
date: "put the date here"
output: html_document
---

```{r include=FALSE,echo=FALSE}
require(tidyverse)
require(tigerstats)
abac <-read.csv(file="abacavirinol.csv",header=TRUE)
Female <- filter(abac,sex=="F")
Male <- filter(abac,sex=="M")
Druggies <- filter(abac,Ivdrug=="user")
LGBT <- filter(abac,LBGT=="yes")
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?.  If you skimp in this section expect to be marked down in your grade. Paint a picture of the project a couple of paragraphs is expected!-->

A new  preventative aides (abacavirinol) is under test in clinical trials. Analyze the effectiveness of this drug across the board. Consider population subgroups by gender, drug use, and sexual orientation. We will consider the population as a whole then in four different subgroups which are females, males, druggies and LGBT.

# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method. Discuss what data manipulations may be needed for example subsetting or other binning procedures and what sort of graphical displays and inferential tools will be used!-->
  
 To analyze the effectiveness of abacavirinol we are looking at the data of each population subgroups:Female, Male, Druggies and LGBT. We recognize that our variables have categoricaland categorical data therefore we will be using barcharts for our graphical data, row&column percent for our numerical data and the chi-square test and fisher test for our inferential results. The chi-sqaure test will evaluate if there is significant assiociation bewtween two categorical variables. 

#Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question. Bottom line is to explain the features of the graph that are relevant to conforming or departing to what is expected by your null hypothesis !-->
```{r}
results <- xtabs(~infected+treatment,data=abac)
barchartGC(results,type = "percent")
```
  
 The barchart displays that drug is probably working beacuse more people that took the placebo got aids compared to those who took the drug abacavirinol. There are about 20 percent of people that got aids with the placebo.   
  
### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
colPerc(results)
rowPerc(results)
```
  
  Out of those who took the drug only about 4 percent got aids and 95.96 were not infected. Meanwhile out of those who took the placebo, 5.54 got aids and 94.46 were not infected. 

## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

```{r}
chisqtestGC(results, graph = TRUE)
```
    
  The chi-sqaured results show that the chi-square statistic is 5.7138. The expected value with degree of freedom is 1. The chi-squared statistic is bigger than the expected value. The p value is 0.0168, which is low therefore we can reject the null hypothesis that the drug doesn't work.

```{r}
fisher.test(results)
```
  
  The fisher test results show that the odds ratio is 0.7181794. The odds are 7 to 1. Your chances of not getting aids is better if you take the drug. 
  
  
# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->
  
  To analyze the effectiveness of the drug Abacavirinol we looked at barcharts, numerical data results, chi-squares test results and fisher test results of the popluation who took the drug vs the placebo. From these results we can conclude that your chances of not getting aids is better if you take the drug. There was more people that were not infected and took the drug and the p value was low therefore we can reject the null the hypothesis and accept the alternative hypothesis that the drug is probably working. 
 
#Female
#Results

## Descriptive Results

### Graphical Descriptive Results

```{r}
results <- xtabs(~infected+treatment,data=Female)
```
```{r}
barchartGC(results,type = "percent")
```
  
  This barchart shows that more females that have aids had taken the drug. It looks as if there iS a 20% difference between the females with aids that took the drug and those who took the placebo.
  

### Numerical Descriptive Results

```{r}
colPerc(results)
rowPerc(results)
```
  
  Out of the females who took the drug, 3.96 were infected with aids while 96.04 did not. Out of the females  who took the placebo 2.59 got aids while 97.41 were not infected.
  
## Inferential Results

```{r}
chisqtestGC(results, graph = TRUE)
```
  
  The chi-squared test results show that the chi-squared statistic is 3.4843. The expected value with degrees of freedom is 1. The chi-squared statistic is slightly greater than the expected value. The p value is 0.062 which is slightly over 0.05 so its not significant. 
  
```{r}
fisher.test(results)
```
  
  The fisher test results show that the odds ratio is 1.548757. In this case the odds of exposure is almost about the same for cases and controls. 

# Discussion and Conclusion
  
  To analyze the effectiveness of the drug Abacavirinol, we looked at graphical, numerical, and inferential data results of women who took the drug vs placebo. From the barchart, the drug does not seem to be too effective. However there is not enough evidence to reject the null hypothesis.

#Male
#Results


## Descriptive Results

### Graphical Descriptive Results

```{r}
results <- xtabs(~infected+treatment,data=Male)
barchartGC(results,type = "percent")
```
  
  This barchart displays that most of the people who got aids took the placebo. This supports that the drug is probably working because of those who were infected with aids, most of them took the placebo and less took the drug.
  
### Numerical Descriptive Results

```{r}
colPerc(results)
rowPerc(results)
```
  
  Of the males who took the drug 30.46% of them were infected with aids however 49.86% were not. Of the males that took the placebo 69.54% got aids and 50.14% did not. More males that took the placebo had aids than those who took the drug. 
  
## Inferential Results

```{r}
chisqtestGC(results, graph = TRUE)
```
  
  The chi-squared test results demonstrate that the chi-squared statistic is 20.4718. The expected value with degrees of freedom is 1. The test statistic is greater tha nthe expected value. The p value in this result is 0.
  
```{r}
fisher.test(results)
```
   
   The fisher test results display the odds ratio is 0.4407101. The odds are 4 to 1. You reduce the chances of getting aids by taking the drug. 
   
# Discussion and Conclusion
  
  We used barcharts, numerical data, chi squared test and fisher test results to analyze the effectiveness of the drug Abacavirinol. From the results we saw that more men who took the drug were not infected and more of those who took the placebo were infected with aids. The results allow us to reject the null hypothesis. Due to the face that more men that took the drug didn't get aids, the drug is probably working.

#Druggies 
#Results

## Descriptive Results

### Graphical Descriptive Results


```{r}
results <- xtabs(~infected+treatment,data=Druggies)
barchartGC(results,type = "percent")
```
  
  This barchart shows that there is a significant difference between those are drugs that took Abacavirinol vs those that took the placebo. Only a few that took the drug had aids however there was way more druggies that took the placebo and got aids. This suggests that the drug is working. 
  
### Numerical Descriptive Results

```{r}
colPerc(results)
rowPerc(results)
```
  
  The numerical results show that of the druggies that took the placebo, 74.36% were infected with aids. 45.66% of those who took the drug were not infected with aids. 
  

## Inferential Results

```{r}
chisqtestGC(results, graph = TRUE)
```
  
  The chi-squared results show that the chi-squared statistic is 5.1942. The test statistic is greater than the expected value. The p value is 0.0227. Since the p value is low, we reject the null hypothesis. 

```{r}
fisher.test(results)
```
  
  The fisher test results show that the odds ratio os 0.410895. The odds are 4 to 1. Your chance of not getting aids is higher if you take the drug.

# Discussion and Conclusion
  
  To analyze the effectiveness of the drug we looked at barcharts, numerical data results, chi-squared test results and fisher test results of druggies who took the drug Abacavirinol vs the placebo. The p value is low and results show that more druggies who took the placebo were infected with aids rather than those who took the drug, therefore we ca reject the null hypotesis and accept the alternative.

#LGBT 
#Results

## Descriptive Results

### Graphical Descriptive Results

```{r}
results <- xtabs(~infected+treatment,data=LGBT)
barchartGC(results,type = "percent")
```
  
  This barchart shows that about 65% of people in the LGBT community that took the drug were infected with aids and about 30% that took the placebo were also infected. However the people in the LGBT community that were not infected, about the same amount either took the drug or placebo. 
  
### Numerical Descriptive Results

```{r}
colPerc(results)
rowPerc(results)
```
  
  The numerical results show that more people in the LGBT community who took the drug got aids rather than those who took the placebo. 50.17% of them were not infected and 49.83% of people who took the placebo were not infected as well. 

## Inferential Results

```{r}
chisqtestGC(results, graph = TRUE)
```
  
  The chi-squared test results show the chi-sqaure statistic is 3.1843. The chi-square statistic is greater than the expected value. The p value os 0.0743 and is not significant. The drug did not show significant efffectiveness so we fail to reject the null hypothesis. 
  
```{r}
fisher.test(results)
```
   
   The fisher test results show that the odds ratio is 2.203969. People in the LGBT community that took the drug still had about 2,20% risk of getting aids. 
   
# Discussion and Conclusion
  
  To analyze the effectiveness of the drug Abacavirinol we looked at barcharts, numerical data results, chi-squares test results and fisher test results of people in the LBGT community that took the drug vs placebo. From these results we can conclude that the drug did not show a significant amount of effectiveness and we fail to reject the null hypothesis. 
  


